\thetitle

### 2020-11-21 writing/results.tex
results: reword to save space

We run the experimental process from section~\ref{sec:rational} on the
sampled debugging scenarios from section~\ref{sec:sample} using a machine with two Intel Xeon Gold 6258R processors and 500GB of memory.
Each debugging scenario had a timeout limit of 4 minutes and a
memory limit of 6GB. The complete experiment required
over 30,000 hours of compute hours on our machine.

Figure~\ref{fig:avo-matrix} summarizes our results and provides answers to
the four questions from section~\ref{subsec:experiment}.  Specifically, it
depicts a head-to-head comparison of the usefulness of each mode against
every other mode.  The cell in row $R$ and column $C$ plots the percentage
of interesting debugging scenarios for which $R$ is more useful $C$ ---
this percentage has been calculated as an estimated proportion from the
corresponding proportion of the debugging scenarios in our sample and the
upper bound.  In effect, reading across a given row $R$ provides an
overview of how $R$ compares to every other mode; the higher the bars, the
more interesting debugging scenarios for which $R$ is strictly more useful
than the other modes.  Reading down a given row $C$ provides an overview
of how every other mode compares to $C$; the higher the bars, the more
interesting debugging scenarios for which $C$ is strictly less useful than
the other modes. For example, the second cell in the row of Natural blame
shows that Natural is more useful than Natural exceptions for 12\% of all
the interesting debugging scenarios we generate from our benchmarks and
mutators.

>>>>

We run the experimental process from section~\ref{sec:rational} on the
sampled debugging scenarios from section~\ref{sec:sample} using a machine with two Intel Xeon Gold 6258R processors and 500GB of memory.
Each debugging scenario had a timeout limit of 4 minutes and a
memory limit of 6GB. The complete experiment required
over 30,000 hours of compute hours.

Figure~\ref{fig:avo-matrix} summarizes our results and provides answers to
the four questions from section~\ref{subsec:experiment}.  Specifically, it
depicts a head-to-head comparison of the usefulness of each mode against
every other mode.  The cell in row $R$ and column $C$ plots the percentage
of interesting debugging scenarios for which $R$ is more useful $C$ ---
we calculate this percentage as an estimated proportion from our sample.
In effect, reading across a given row $R$ provides an
overview of how $R$ compares to every other mode; the higher the bars, the
more interesting debugging scenarios for which $R$ is strictly more useful
than the other modes.  Reading down a given row $C$ provides an overview
of how every other mode compares to $C$; the higher the bars, the more
interesting debugging scenarios for which $C$ is strictly less useful than
the other modes. For example, the second cell in the row of Natural blame
shows that Natural is more useful than Natural exceptions for 12\% of all
the interesting debugging scenarios we generate from our benchmarks and
mutators.
